What if you drop that? Modeling children's curiosity about physical interactions

### 2020-01-26 paper/paper.Rmd
more updates to 3rd para of intro

The goal of the current paper is to help close this gap by proposin a framework for advancing our theoretical understanding of curiosity that combines three key ingredients: _first_, we present a computational theory of how a learner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior; _second_, we present an empirical investigation of the pattern of actions taken by children in a novel physical exploration task; and _third_, we evaluate the quantitative correspondence between the exploratory actions taken by our computational theory and those taken by children on the same set of tasks.

@@

<!-- First, we need a precise mechanism that specifies how stimuli inspire curiosity.  -->
Our computational theory is inspired by classic verbal theories that posited that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954,@Fantz1964], as well as other verbal theories proposing to explain curiosity-driven behavior as the manifestation of learners' preferences for stimuli that are "moderately discrepant" in comparison to our mental representations, and thereby provide opportunities to learn [@Kinney1976]. Recent studies have provided empirical support for this basic idea: XX-old infants are sensitive to stimulus complexity and prefer to look at moderately complex stimuli rather than overly simple or overly complex stimuli; @Kidd2012; @Kidd2014].
Thus, these theories hold that curiosity is inspired by awareness of a knowledge gap [@Loewenstein1994], and that as our mental representations mature our preferences will tend toward more complex stimuli [@Dember1957].
On these accounts, similar to other drives (e.g., hunger), curiosity is sated as relevant information is gained and the knowledge gap is closed. However, these theories have yet to define these perceptual and knowledge-based representations or specify how they are compared.

>>>>

The goal of the current paper is to help close this gap by proposin a framework for advancing our theoretical understanding of curiosity that combines three key ingredients: _first_, we present a computational theory of how a lerner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior; _second_, we present an empirical investigation of the pattern of actions taken by children in a novel physical exploration task; and _third_, we evaluate the quantitative correspondence between the exploratory actions taken by our computational theory and those taken by children on the same set of tasks.

@@

<!-- First, we need a precise mechanism that specifies how stimuli inspire curiosity.  -->
Our computational theory is inspired by classic descriptive theories that posited that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954,@Fantz1964], as well as theories providing qualitative explanations for curiosity-driven behavior as the result of learners' preferences for stimuli that are "moderately discrepant" in relation to their current knowledge state, and thereby provide opportunities to learn [@Kinney1976]. Recent studies have provided empirical support for this basic idea: XX-old infants are sensitive to stimulus complexity and prefer to look at moderately complex stimuli rather than overly simple or overly complex stimuli; @Kidd2012; @Kidd2014].
According to these theories, curiosity-driven behavior reflects a gap between the learner's knowledge and the state of the world [@Loewenstein1994], and thus they predict that as a learner gains additional knowledge, their preferences will shift toward more complex stimuli [@Dember1957].
<!-- Moreover, curiosity is thought of as being similar to other basic drives (e.g., hunger) in that learners are thought to become sated as relevant information is acquired and the knowledge gap is closed.  -->
Although these theories have provided important qualitative insights, one of their major limitations is that they do not provide precise ways to characterize a learner's current knowledge state, how physical states of the world are represented in their mind, nor how discrepancies between a learner's knowledge and such states are compared.
